Sorting by Reversals

### 2020-07-12 paper.tex
update paper conclusion

We have seen multiple layers of abstraction that allowed us to describe a $3/2$-approximation. As was mentioned in the introduction, a better but more complex approximation was obtained later by \citeauthor*{Berman2001}.

An interesting property of the discussed $3/2$-approximation is that when constructing the alternating cycle decomposition, any cycle decomposition of the edges that are not part of $2$-cycles will suffice \cite{Christie1998}.

>>>>

We have seen the fundamental relationship between the reversal distance of a permutation and its number of breakpoints as well as the maximum number of alternating cycles of a cycle decomposition of its breakpoint graph as was first discussed by \citeauthor*{Bafna1996}. Exploiting this relationship, \citeauthor*{Christie1998} described a $3/2$-approximation we discussed in detail. A better but more complex approximation was obtained later by \citeauthor*{Berman2001}.

An interesting property of the described $3/2$-approximation is that when constructing the alternating cycle decomposition, any cycle decomposition of the edges that are not part of $2$-cycles will suffice \cite{Christie1998}.
